Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-12 doc/report/msc-report.tex
subsection{Internal Data Interchange}

\section{Data Interchange}

The reducer needs to communicate to the OutputReader under what row key,
column-family and qualifier to store the computed sum. It does this by
emitting the row key as the key and a JSON-serialized map of the form \\
\texttt{\{"column-family:qualifier" : value\}}.

The OutputReader interprets the JSON and persists the data. Et voila!

\subsection*{Internal}

Using JSON for data interchange between map and reduce parts in Zohmg import
jobs.

For better performance typed bytes may be used. This is what Dumbo uses
internally.

\subsubsection{Input Formats}

An input format is a Java class which Hadoop uses for interpreting the input
data.

The simplest input format would be the TextInputFormat, this is used to parse
flat text files which reside on HDFS.

Hadoop is able to read LZO compressed files with the LzoInputFormat. In order to
be able to do so effectively the compressed files first have to be indexed with
a tool that is provided with Hadoop.

% TODO: When is the TableInputFormat used.
The TableInputFormat is able read input to a Hadoop program from an HBase table.

\subsubsection{Output Formats}

% TODO: not truly correct
% TODO: A detailed explanation of generally everything in the darling dir.
The Darling output format for HBase. Between Dumbo, which Zohmg uses for data
import, and JSON is used for serializing data.

The Darling output format increased import speed by a factor ten, compared to
using Thrift. The HBase Thrift interface is slow because it first spawns a Java
HBase client which interprets everything from the HBase Thrift server.
This actually adds an extra step to the interaction with HBase making it slower
than talking to it natively with Java.

>>>>

\subsection{Internal Data Interchange}

The reducer needs to communicate to the output reader under what row and column
the computed aggregate is to be stored. The reducer does this by emitting the
row key as key, and a JSON-serialized hash table, which is called a dict in
python, as value. The structure of the map is of the form \\
\texttt{\{"column-family:qualifier" : value\}}.

The output reader, which is a Java class that is executed within the Hadoop
framework, de-serializes the JSON structure and constructs an HBase object that
is persisted to the underlying HBase data store.
